Harmonized Finnish National Bibliography

### 2022-11-16 inst/examples/index.Rmd
Bookdown compatibility

--- 
title: "Harmonized Finnish National Bibliography"
author: "`r author`"
date: "`r Sys.Date()`"
site: "bookdown::bookdown_site"
output:
  bookdown::gitbook: default
documentclass: book
---

In this bookdown project we will disseminate the fennica dataset cleaning process.

@@

>>>>

--- 
title: "Harmonized Finnish National Bibliography"
author: "Helsinki Computational History Group (COMHIS)"
date: "`r Sys.Date()`"
site: "bookdown::bookdown_site"
output:
  bookdown::gitbook: default
documentclass: book
---

# Preface

In this bookdown project we will disseminate the Finnish National Bibliography (fennica) bibliographic dataset cleaning process.

@@

This document was generated with the following packages:

```{r system-information}
sessionInfo()
```
